Differential Expression

### 2020-04-05 cmc-rnaseq-de/Differential-Expression.Rmd
header = T in fread

### Data download
#### Obtain filtered and CQN normalized counts
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}

>>>>

### Data download
#### Obtain filtered and CQN normalized counts
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F, header = T)
}
